Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-03-15 journal-draft/bare_jrnl_comsoc.tex
licensed->licensed

We consider wireless sensor nodes distributed on a two-dimensional Euclidean plane. We denote the set of these nodes as $V$ which is partitioned into sets of primary users $V_P$ and secondary users $V_N$, i.e., $V~=~V_P~\dot\cup~V_N$. These users share a number of non-overlapping licenced channels according to the spectrum overlay model. The set of these licenced channels is denoted as $\mathcal{C}$. Secondary users are allowed to transmit on a channel $c \in \mathcal{C}$ only if every primary user $p \in V_P$ that has access to channel $c$ is idle. Further, we consider a \textit{cognitive radio ad-hoc network} which consists of all secondary users and does not contain any primary user.

@@

Secondary users conduct spectrum sensing independently and sequentially on all licenced channels. In our system model, we assume that a secondary node $n$ is able to detect for each channel $c$ whether any primary user utilizes $c$. We denote $C_n \subseteq \mathcal{C}$ as the set of available channels for $n$.

@@

In addition to the licenced channels there is one dedicated control channel. It is available for any secondary node $n$ to exchange control messages with any other node in its proximity (or neighborhood) $N(n)$ during the cluster formation phase. $N(n)$ is simply defined as the set of nodes located within the transmission range of $n$. Control messages involved in the clustering process can be transmitted on available licenced channels through a rendez-vous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}. \textcolor{red}{(The rendez-vous should be briefly explained! TODO)} Over the control channel, a secondary user $n$ can exchange its spectrum sensing result $C_n$ to any $n' \in N(n)$.

>>>>

We consider wireless sensor nodes distributed on a two-dimensional Euclidean plane. We denote the set of these nodes as $V$ which is partitioned into sets of primary users $V_P$ and secondary users $V_N$, i.e., $V~=~V_P~\dot\cup~V_N$. These users share a number of non-overlapping licensed channels according to the spectrum overlay model. The set of these licensed channels is denoted as $\mathcal{C}$. Secondary users are allowed to transmit on a channel $c \in \mathcal{C}$ only if every primary user $p \in V_P$ that has access to channel $c$ is idle. Further, we consider a \textit{cognitive radio ad-hoc network} which consists of all secondary users and does not contain any primary user.

@@

Secondary users conduct spectrum sensing independently and sequentially on all licensed channels. In our system model, we assume that a secondary node $n$ is able to detect for each channel $c$ whether any primary user utilizes $c$. We denote $C_n \subseteq \mathcal{C}$ as the set of available channels for $n$.

@@

In addition to the licensed channels there is one dedicated control channel. It is available for any secondary node $n$ to exchange control messages with any other node in its proximity (or neighborhood) $N(n)$ during the cluster formation phase. $N(n)$ is simply defined as the set of nodes located within the transmission range of $n$. 
Control messages involved in the clustering process can be transmitted on available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., . \textcolor{red}{(The rendez-vous should be briefly explained! TODO)} Over the control channel, a secondary user $n$ can exchange its spectrum sensing result $C_n$ to any $n' \in N(n)$.
